A thesis draft

### 2018-11-12 res/sections/08-Background.tex
Reword todo

\section{Virtualization}
Cloud computing is now a leading-edge Internet technology and the virtualization
technology is one of the most important part of cloud computing systems.
Virtualization, in computing, refers to the act of creating a virtual (rather
than an actual) version of something, including but not limited to a virtual
computer hardware platform, operating system (OS), storage device, or computer
network resources. \todo{To change I do not what can I write, stolen from ``The
research and implementation of cloud computing platform based on docker'' paper}

>>>>

\section{Virtualization}
Cloud computing is now a leading-edge Internet technology and the virtualization
technology is one of the most important part of cloud computing systems.
Virtualization, in computing, refers to the act of creating a virtual (rather
than an actual) version of something, including but not limited to a virtual
computer hardware platform, operating system (OS), storage device, or computer
network resources. \todo{This part was taken from ``The research and
implementation of cloud computing platform based on docker'' paper, rework it
in a way it doesn't seem to be copied.}
